\chapter{Background (18)}
\label{ch:background}

The aim of this chapter is to give the reader background information on the problem domain in order for them
to understand the rest of the report.
This will consist first of an introduction to machine learning.
Then we will go into more detail on the areas of reinforcement learning and texas hold'em.
Finally we will take a deeper dive on the literature surrounding how we can utilise reinforcement learning
to tackle the problem of texas hold'em.

\section{Introduction to Texas Hold'em}\label{sec:thIntro}
Texas hold'em is one variant of the family of games called poker.
Poker is a group of card games that combine gambling, strategy and skill.
All poker variants have three core similarities.
There is betting involved, there is imperfect information (ie cards remain hidden until the end of a hand)
and the winner is determined by combinations of cards.
We will now discuss texas hold'em poker in more detail.

\subsection{Game Structure}\label{subsec:bettingRounds}
Texas hold'em consists of four betting rounds.
Initially each player is dealt two private cards.
These remain face down and only the person who received these cards may view them.
In the next three rounds five public cards are dealt face up on the table.
The second round of dealing is called the flop, where three cards are dealt.
The third round is called the turn where one additional public card is dealt.
Finally in the fourth round another card is dealt which is called the river.

At each round, after the cards are dealt, the players are given the opportunity to take a number of betting related actions.
We will discuss the permitted actions in the next section.

In order for players to be incentivized to continue playing in a wider array of situations, blinds are required.
Blinds are a mandatory bet that must be posted by two of the players present at the game.
These two bets are called the big blind and the small blind, the big blind being twice that of the small blind.
As hands are played the big and small blinds are posted by different players in order to distribute the cost fairly.

The big and small blind are the first two bets that contribute to what's called the pot.
The pot is the collection of all of the current chips bet by the players.
When a player wins a hand then what they receive in return is the pot.

The final structural component of the game is player stacks.
Each player will start the game with a certain amount of chips.
If a player wins a pot then all of the chips in the pot are transferred to the winners stack.
\subsection{Actions}\label{subsec:actions}
\subsection{Hand Values}\label{subsec:handValues}

\section{Introduction to Machine Learning (1) w6}\label{sec:introductionToMachineLearning}

Machine learning is an area of computer science that tackles how we construct computer programs that improve
with experience\cite{mitchell1997machine}.
The term was coined by Arthur Samuel in his 1959 paper where he discussed machine learning methods using
checkers as his problem area.
Since then there has been a great deal of advancement in the field.
Some of the notable early contributions being the discovery of recurrent neural networks in 1982 and
the advancement of reinforcement learning by the introduction of Q-Learning in 1989.
Recently we have seen some of this early academic work culminate in more practical achievements such as
Facebook's DeepFace system which, in 2014,  was shown to be able to recognise faces at a rate of 97.35\% accuracy,
a rate that is comparable to that of humans.
Another example of recent achievement is Google's AlphaGo program which, in 2016, became the first program to beat
a professional human player.

It should be becoming clear that machine learning can be a solution to a wide scope of problems and as
both hardware and software continue to improve this scope will only continue to widen.
We are starting to see machine learning systems become a key component of many companies business model.
Since certain machine learning techniques are great at prediction, machine learning has been widely used
for content discovery by companies such as Google and Pinterest.
Other business applications include the use of chatbots as a part of customer service, self-driving cars
and even in the field of medical diagnostics.

Since there is such a large range of actual and potential applications for machine learning it would be good for
us to understand how different methodologies can be applied to solve different types of problems.
In the next we will discuss just that.


\section{Machine Learning Categories (3) w6}\label{sec:mlCategories}

\subsubsection{Supervised Learning}
Supervised learning involves an agent which observes some example input-output pairs and learns
a function that maps from input to output.\cite{russell2016artificial}.
This learned function can then be used on new input data, that wasn't used to train the agent and the
agent should be able to give an accurate output.
As such this learning task is a generalization problem.
The agent must be able to identify general features of the input data and how they map to the output.
Common examples of 


\subsubsection{Unsupervised Learning}
\subsubsection{Reinforcement Learning}


\section{Applications of Reinforcement Learning (1) w7}\label{sec:rlApplications}


\section{Reinforcement Learning Methods (9) w7}\label{sec:rlMethods}

\subsection{Dynamic Programming (3)}\label{subsec:dp}

\subsection{Monte Carlo (3)}\label{subsec:mc}

\subsection{Temporal Difference Learning (3)}\label{subsec:td}


\section{Reinforcement Learning In Large State Spaces (1) w7}\label{sec:rlLargeStateSpace}